---
title: "Cats vs. Dogs"
output: html_notebook
---

To install missing packages, run `install.packages("package_name")`
```{r setup}
# Packages ----
library(tidyverse)
library(plotly)

# Plot settings ----
theme_set(theme_bw())

# Knitr options ----
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

# Cats vs. Dogs
## Data
Read data in from URL.
```{r data}
catsvdogs <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018-09-11/cats_vs_dogs.csv") %>% 
  select(-X1)
```

Check data names.
```{r}
names(catsvdogs)
```

Look at first 6 rows of data.
```{r}
head(catsvdogs)
```

## EDA
Which state has the highest `avg_dogs_per_household`?
```{r}
catsvdogs %>% 
  arrange(desc(avg_dogs_per_household)) %>% 
  select(state, avg_dogs_per_household)
```

Which state has the highest `avg_cats_per_household`?
```{r}
catsvdogs %>% 
  arrange(desc(avg_cats_per_household)) %>% 
  select(state, avg_cats_per_household)
```

Is there a correlation between dog ownership and cat ownership?
```{r}
percent_owners_plot <- catsvdogs %>% 
  filter(state != "District of Columbia") %>% 
  ggplot(aes(x = percent_dog_owners, y = percent_cat_owners)) +
  geom_point(aes(col = state), show.legend = FALSE) +
  geom_smooth(se = FALSE, method = "lm")

ggplotly(percent_owners_plot)
```

How do we represent this geographically? (follow example outlined [here](https://plot.ly/r/choropleth-maps/))
```{r}
# Add state code to the data
catsvdogs <- catsvdogs %>% 
  merge(
    tibble(state = state.name,
           code = state.abb)
  )

g <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showlakes = TRUE,
  lakecolor = toRGB('blue')
)

catsvdogs %>% 
  plot_geo(locationmode = 'USA-states') %>%
  add_trace(
    z = ~percent_cat_owners, locations = ~code,
    color = ~percent_cat_owners, colors = 'Reds'
  ) %>%
  colorbar() %>%
  layout(
    title = 'Cat Ownership in the USA',
    geo = g
  )
```

```{r}
catsvdogs %>% 
  plot_geo(locationmode = 'USA-states') %>%
  add_trace(
    z = ~percent_dog_owners, locations = ~code,
    color = ~percent_dog_owners, colors = 'Blues'
  ) %>%
  colorbar() %>%
  layout(
    title = 'Dog Ownership in the USA',
    geo = g
  )
```

Calculate and plot rankings based on difference between `percent_dog_owners` and
`percent_cat_owners`.
```{r}
catsvdogs %>% 
  mutate(perc_diff = percent_dog_owners - percent_cat_owners,
         color = perc_diff > 0) %>% 
  arrange(desc(perc_diff)) %>% 
  mutate(row_num = row_number(),
         state = glue::glue("{state} ({row_num})")) %>% 
  ggplot(aes(x = fct_reorder(state, perc_diff), y = perc_diff, fill = color)) +
  geom_col(show.legend = FALSE) +
  labs(x = "",
       y = "Percent difference in dog owners and cat owners",
       title = "Dog lovers of America unite") +
  coord_flip()
```

What's going on with Delaware?
```{r}
catsvdogs %>% 
  filter(state == "Delaware") %>% 
  select(contains("percent"))
```

# College Majors
## Data
Read in data from URL and clean up names using the
[`janitor`](https://github.com/sfirke/janitor) package
```{r}
college_majors <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018-10-16/recent-grads.csv") %>% 
  janitor::clean_names(case = "snake")
```

Check data for any problems with parsing
```{r}
problems(college_majors)
```

Take a look at the data using `View()`
```{r}
View(college_majors)
```

What are the highest/lowest earning majors?
```{r}
earnings_order <- college_majors %>% 
  select(major, median) %>% 
  arrange(desc(median))

earnings_order %>% 
  head() %>% 
  bind_rows(
    earnings_order %>% 
      tail()
  )
```

What about Statistics?
```{r}
college_majors %>% 
  filter(str_detect(tolower(major), "stat")) %>% 
  select(major, median)
```

Plot median salary by major.
```{r}
college_majors %>% 
  ggplot(aes(x = fct_reorder(major, median), y = median)) + 
  geom_col() + 
  scale_y_continuous(labels = scales::dollar) +
  labs(y = "Median Salary",
       x = "",
       title = "Major Median Salaries") +
  coord_flip()

```

How many of each `major_category` are there?
```{r}
college_majors %>% 
  count(major_category, sort = TRUE)
```

What's the distribution of median income across each `major_category`?
```{r}
college_majors %>% 
  ggplot(aes(x = fct_reorder(major_category, median), y = median)) +
  geom_boxplot() +
  scale_y_continuous(labels = scales::dollar) +
  labs(y = "Median Income",
       x = "",
       title = "Income Distribution across Major Categories") +
  coord_flip()
```

```{r}
college_majors %>% 
  ggplot(aes(x = fct_reorder(major_category, share_women, na.rm = TRUE), y = share_women)) +
  geom_boxplot() +
  scale_y_continuous(labels = scales::percent) +
  labs(y = "% Women",
       x = "",
       title = "Percentage of Women by Major Category") +
  coord_flip()
```

