---
title: "Stat 123 Review"
output: html_notebook
---

## Using RStudio Projects
Using RStudio projects makes life in R much easier. When done correctly, this 
means that you will not need to use `setwd()` in your code. You can read more
about the advantages of using Projects [here](https://www.tidyverse.org/articles/2017/12/workflow-vs-script/).

## Vectorization
One of R's strengths is the fact that it is vectorized, which means that R will
often automatically apply operations to every element of a provided vector. As
an example, consider the vector `x <- 1:10`. If we want to add 1 to each element,
we could do the following:

```{r}
x <- 1:10
y <- numeric()
for (i in 1:length(x)) {
  y[i] <- x[i] + 1
}

y
```

However, that is bad practice in R since it does not take advantage of R's
notion of vectorization. We could have simply done the following:

```{r}
x + 1
```

## Functions

Functions are used to create pieces of code that can be re-used with different
parameter values.

Functions can be defined inline:
```{r}
# Function whose input is a scalar and output is square of the scalar
square <- function(x) x^2
square(10)
```

Or with curly braces:
```{r}
square <- function(x) {
  x^2
}
square(10)
```

Create a function whose input is a vector of values and whose output is the
mean, median, and variance of the vector of values.  Do this with out using
the "mean", "median", or "var" functions
```{r}
mn_md_var <- function(x) {
	n <- length(x)
	mn <- sum(x)/n
	var <- sum((x - mn)^2)/(n - 1)
	sx <- sort(x)
	md <- if (n %% 2 == 1) {
		sx[floor(n/2) + 1]
	} else {
		(sx[n/2] + sx[n/2 + 1])/2
	}
	c(mn, md, var)	
}
```

Write a zero function (i.e., a function that always returns 0)
```{r}
zero <- function(x) 0
zero(60)
zero(100)
zero("a")
```

## Iteration
Like most, if not all, programming languages, R has the ability to create loops.
A loop simply re-executes a defined code expression a set number of times (for 
loop) or until a specific condition is met (while loop).

```{r}
x <- FALSE
i <- 1
while (!x) {
  print(paste("Try", i))
  x <- sample(c(TRUE, FALSE), 1)
  i <- i + 1
}
```

The `apply` family of functions provide convenient methods for iterating over the
elements of an object and performing some function on each element.

```{r}
x <- 1L:10L
sapply(x, function(x) x^2)
lapply(x, function(x) x^2)
```

Note that in the example above, we could have also simply done `x^2`, which would
be the ideal way to accomplish this specific task in R.

The `purrr` package provides additional tools for functional programming and 
iteration in R.

```{r}
library(purrr)
map(x, ~.^2)
map_int(x, ~as.integer(.^2))
```

## Plotting
There are two main conventions commonly used for plotting in R: base R graphics 
and `ggplot2`. In this course we will use a mixture of both - base graphics at
times for convenience and `ggplot2` when we need a better lookign and/or more 
flexible plot.

As an example, we'll create a histogram of some random values from the standard
normal distribution.

```{r}
x <- rnorm(1000)
```

```{r}
hist(x, main = "My Histogram", col = "grey", xlab = "X Values")
legend("topright", "Legend")
```

```{r}
library(ggplot2)
ggplot(data.frame(x = x), aes(x = x)) +
  geom_histogram(fill = "grey", col = "black") +
  labs(title = "My Histogram",
       x = "X Values") +
  theme_bw()
```
