---
title: "Confidence Intervals"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE)
```

> More strictly speaking, the confidence level represents the frequency (i.e. the 
proportion) of possible confidence intervals that contain the true value of the 
unknown population parameter. In other words, if confidence intervals are constructed
using a given confidence level from an infinite number of independent sample 
statistics, the proportion of those intervals that contain the true value of the 
parameter will be equal to the confidence level.

\- [Wikipedia](https://en.wikipedia.org/wiki/Confidence_interval)

---

Create a function to compute a confidence interval assuming the population is
normally distributed. By default, `sd = NA` and `confidence_level = 0.95`. The
function will take a numeric vector `x` and produce a 95% confidence interval
using a t-table value (since the population standard deviation is missing) with
degrees of freedom equal to the length of `x` - 1.

When the population standard deviation is known and supplied, the calculation will
be based on a standard normal table value.

```{r}
confidence_interval <- function(x, sd = NA, confidence_level = 0.95) {
  alpha <- 1 - confidence_level
  if (!is.na(sd)) {
    table_value <- qnorm(alpha/2, lower.tail = FALSE)
  } else {
    table_value <- qt(alpha/2, df = length(x) - 1, lower.tail = FALSE)
    sd <- sd(x)
  }
  ci <- mean(x) + c(-1, 1) * table_value * sd / sqrt(length(x))
  names(ci) <- c("Lower Bound", "Upper Bound")
  ci
}
```

Now, let's calculate some confidence intervals on known distributions.

```{r}
n <- 5
true_mean <- 0

# Define the population - drawing from a standard normal distribution
data <- rnorm(n, true_mean, 1)
data
```

```{r}
interval <- confidence_interval(data)
interval
```

This is our confidence interval for the mean of the simulated data we just created. We can check to see if this interval includes the `true_mean`.

```{r}
interval[1] < true_mean && true_mean < interval[2]
```

Now, let's run it again!

```{r}
data <- rnorm(n, true_mean, 1)
data

interval <- confidence_interval(data)
interval
```

Why are these confidence intervals different?

### Simulation
Now we'll simulate thousands of confidence intervals!

```{r}
n_reps <- 10000
```


#### For Loop
```{r}
contains <- numeric(n_reps)
intervals <- matrix(NA, nrow = n_reps, ncol = 2)
for (i in 1:n_reps) {
  data <- rnorm(n, true_mean, 1)
  interval <- confidence_interval(data)
  intervals[i,] <- interval
  contains[i] <- interval[1] < true_mean && true_mean < interval[2]
}

coverage <- mean(contains)
coverage
```

#### Replicate
```{r}
intervals <- replicate(n_reps, {
  data <- rnorm(n, true_mean, 1)
  confidence_interval(data)
})

contains <- apply(intervals, 2, prod) < 0

coverage <- mean(contains)
coverage
```

#### Tidyverse
```{r}
library(tidyverse)

intervals <- rerun(n_reps, confidence_interval(rnorm(n, true_mean)))

contains <- map_lgl(intervals, ~prod(.) < 0)

coverage <- mean(contains)
coverage
```


Look at that! Close to .95 - illustrating exactly what the definition of a confidence interval refers to. Now, since we arrived at this calculation via a simulation, we can put a confidence interval on our coverage estimate for confidence intervals. Now, note that in this case we're creating a confidence interval for a proportion:

$$
p \pm Z_\alpha \sqrt{\frac{p(1-p)}{N}}
$$

```{r}
coverage + c(-1, 1) * qnorm(0.975) * sqrt(coverage * (1 - coverage)/n_reps)
```

Now let's get some visual intuition behind this:
```{r}
intervals_df <- map_df(intervals, ~tibble(lower = .["Lower Bound"], upper = .["Upper Bound"])) %>% 
  mutate(index = 1:n(),
         includes = lower <= true_mean & upper >= true_mean)
```

```{r, fig.height=6, fig.width=4}
ggplot(head(intervals_df, 100), aes(x = lower, xend = upper, y = index, yend = index)) +
  geom_segment(lineend = "butt", aes(col = includes), show.legend = FALSE, lwd = 2) +
  geom_vline(xintercept = true_mean, col = "red", lwd = 1.5) +
  theme_bw() +
  labs(title = "Confidence Interval Coverage",
       x = "", 
       y = "")
```



### Expand the simulation
```{r}
simulate <- function(ci_function, truth = 0, n_reps = 10000) {
  # ci_function returns a confidence interval for a given set of data
  cov <- apply(replicate(n_reps, ci_function() - truth), 2, prod) < 0
  coverage <- mean(cov)
  # Confidence interval for proportion
  coverage + c(-1, 1) * qnorm(0.975) * sqrt(coverage * (1 - coverage)/n_reps)
}
```

```{r}
simulate(function() confidence_interval(rnorm(5), sd = 1))
simulate(function() confidence_interval(rnorm(5, sd = 1)))
simulate(function() confidence_interval(rnorm(5, sd = 1), sd = 1.5))
```

```{r}
sapply(c(5, 10, 50, 100, 1000), function(n_observations) {
  simulate(function() confidence_interval(rnorm(n_observations)))
})
```

