---
title: "Practice Midterm"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
    
## Late (55 points)
I want to know if I will make it to my 9:00am class on time at least 70% of the
time. I decided that if I’m on time less than 70% of the time, then I will need
to wake up earlier. I want to run a simulation based on my current process for
getting to school to see how often I make it on time.

First, I walk to the bus station. I leave my apartment between 8:30am and
8:35am. The time I leave my apartment is completely random and follows a uniform
distribution. It takes me 5 minutes to walk to the bus station.

  + Random uniform numbers can be found using `runif()`
  
Second, the bus arrives around 8:39am, but it’s random when it arrives. In fact,
it arrives randomly based on a normal distribution with a mean at 8:39am and a
standard deviation of 2 minutes. After the bus arrives, it waits 30 seconds
until it leaves, with or without me (rude, right?). *If I miss the bus, I will
definitely be late to class.*

  + Random values from a normal distribution can be found using `rnorm()`
  
Third, the bus takes 10 minutes to get to campus with no red lights. However,
there are four traffic lights, each with a 30% chance of being red when we get
to it. For each light that is red, it adds 2 minutes to the bus ride time to
campus (if all four happened to be red, then that would add 8 minutes to the
time and the total bus ride would take 18 minutes).

Finally, once I get to campus, it takes 5 minutes to walk to class.

1. Create a function called `on_time`. This function should simulate a single
instance of going to class and return either `TRUE` or `FALSE`, indicating
whether or not I was on time to class. (20 points)
2. Use the `on_time` function you just created and run this simulation 10,000
times. Store the results in a vector called `on_time_results`. (10 points)
3. Using the `on_time_results` vector you just created, calculate the proportion
of times that you will be on time. (10 points)
4. Build a 95% confidence interval around the value you calculated in step 3.
(10 points)
5. Do I need to wake up earlier? (5 points)

## Bikes (50 points)
You work as a supply chain manager at a up-and-coming bicycle manufacturing
company. One of the main functions of your job is to forecast the demand for
your bicycles so you can purchase enough tires from your suppliers in time to
sell the completed bikes to your distributors. The function that the supply
chain team has derived for forecasting an arbitrary month's bicycle demand is:
$$
FD_m = (1 + (G / 12)) * (AD_{m-1} + AD_{m-12}) / 2
$$

  + $FD_m$ is the forecasted demand for the month in question
  + $G$ is the forecasted yearly growth rate
  + $AD_{m-1}$ is the previous month's actual demand
  + $AD_{m-12}$ is the month in question's actual demand from the previous year
  
It is now December 2018 and you are preparing to forecast the demand for January
2019. The actual monthly demand for 2018 was as follows:

```{r, eval = FALSE}
actual_2018 <- c(
  jan = 200,
  feb = 305,
  mar = 352,
  apr = 327,
  may = 375,
  jun = 407,
  jul = 330,
  aug = 295,
  sep = 275,
  oct = 255,
  nov = 230,
  dec = 450
)
```

You know that $G$ (the yearly growth rate) is impossible to predict due to
recent volatile growth. However, you know that $G$ has historically followed a
normal distribution with $\mu = 0.25$ and $\sigma = 0.15$.

Your team would like to estimate the forecasted demand for January 2019 and find
a 95% confidence interval on the estimate.

1. Write a function called `jan_pred` that returns a single estimate for the
forecasted demand in January 2019. You'll use the forecasting function defined
above. (10 points) 
2. Use the `jan_pred` function you just created and run this simulation 10,000
times. Store the results in a vector called `jan_forecasts`. (10 points)
3. Using the `jan_forecasts` vector, calculate the estimated forecast for
January 2019. (10 points)
4. Build a 95% confidence interval on the estimate you just calculated. (10
points)
5. What is the anticipated growth ratio (January 2019 prediction / January
2018 actual) and its 95% confidence interval? (10 points)
